video-and-reproducible-science

### 2016-04-29 nyu-data-science-reproducibility-16/video-reproducibility.Rmd
Update slides

@@

## Video and Reproducible Workflows

@@

@@

## How Databrary Aids Reproducibility

## Analysis Pipeline Using Databrary

@@

- [Datavyu.org](http://datavyu.org)
- Video coding tool
- Java with Ruby API for [scripting](https://github.com/databrary/Datavyu-Example-Scripts)
- Free, open source, <https://github.com/databrary/datavyu>

@@

## Datavyu Script Example 2

- Bulk export for analysis

@@

- Video captures behavior
- Databrary securely stores, shares video
- Video + Databrary -> reproducible and transparent workflows
- Video + Datavyu -> reproducible and transparent workflows

>>>>

## “Video Doesn’t Lie"

<div class=centered>
**Reproducible Workflows With [Databrary](http://databrary.org)**

Karen E. Adolph (NYU)</br>
David Millman (NYU)</br>
Rick O. Gilmore (Penn State)</br>

<http://github.com/databrary/presentations/nyu-data-science-reproducibility-16/video-reproducibility>
</div>

@@

@@

<div class="centered">
<video width="640" height="480" controls>
  <source src="https://nyu.databrary.org/slot/9840/-/asset/11193/download?inline=true" type="video/mp4">
Your browser does not support the video tag.
</video>
[[@c7fbeef0-d8a9-4b99-9e17-f598507486b7]](http://doi.org/10.17910/B7H019)
</div>

https://nyu.databrary.org/slot/9840/-/asset/11193/download?inline=true

## [[@c7fbeef0-d8a9-4b99-9e17-f598507486b7]](http://doi.org/10.17910/B7H019)

<div class=centered>
<a href="https://nyu.databrary.org/volume/33">
<img src="img/frank-databrary.jpg" height=550px>
</a>
</div>

@@

## Databrary Improves Reproducibility

- "Active" curation of data *as it's collected*
- Organize, share, standardize participant metadata
- Share materials, displays

## Databrary Improves Reproducibility

- External links to code repos
- DOIs for shared datasets
- Long-term preservation via partnership with NYU Libraries

@@

- Most analyses of video use specialized tools
- [Datavyu.org](http://datavyu.org)
- Free, open source, <https://github.com/databrary/datavyu>
- Java with Ruby API for [scripting](https://github.com/databrary/Datavyu-Example-Scripts)

@@

@@

- Video captures behavior
- Databrary securely stores, shares video
- Video + Databrary -> reproducible & transparent workflows
- Video + Datavyu -> reproducible & transparent workflows
- Databrary helps make psychological science more transparent & reproducible
